	\begin{thebibliography}{99}
	
	\bibitem{abra} Abramowitz, M.; Stegun, I. A. (1964) \textit{Handbook of mathematical functions with formulas, graphs, and mathematical tables}. National Bureau of Standards Applied Mathematics Series, 55 For sale by the Superintendent of Documents, U.S. Government Printing Office, Washington, D.C. 1964 xiv+1046 pp. (Reviewer: D. H. Lehmer) 33.00 (65.05)
	
	\bibitem{Adler-The} Adler R. J. (1981), \textit{The geometry of Random Fields}, Wiley and Sons, New York. 
	
	\bibitem{Adler e Taylor} Adler, R. J.; Taylor, J. E. (2007)
	\textit{Random fields and geometry}. Springer Monographs in Mathematics. Springer,
	New York.
	
	% \bibitem{ATW} Adler R. J., Taylor J. E. and Worsley K. J. (2010), \textit{Applications of random fields and geometry: Foundations and case studies}, Available at http://webee.technion.
	%	ac.il/people/adler/publications.html.
	\bibitem{AAR} Andrews G. E, Askey R., Roy R. (1999) \textit{Special Functions Enciclopedia of Mathematics and its Applications}, 71, Cambridge University Press, Cambridge.
	
	\bibitem{AH} Atkinson K., Han W. (2012) \textit{Spherical Harmonics and Approximations on the Unit Sphere: an introduction, Lecture Notes in Mathematics}, 2044, Springer.
	
	
	
	
	\bibitem{Azais e ws} Azais, J. M.; Wschebor, M. (2009) \textit{Level sets
		and extrema of random processes and fields}, Wiley and Sons, New Jersey.
	
	%	\bibitem{BBW} Benatar, J., Buckley, J., Wigman, I. Two applications of Bourgain's de-randomization method on toral eigenfunctions and spectral quasi-correlations, in preparation.
	
%	\bibitem{Baldi} Baldi, P. (2010) Representation of Gaussian isotropic spin random fields. \textit{Physical Review D, 81:083505}. Stochastic Process. Appl. 124 (2014), no. 5, 1910-1941.
	
	\bibitem{BKMP2009} Baldi, P.; Kerkyacharian, G.; Marinucci, D.; Picard, D. (2009). Asymptotics for Spherical Needlets, \textit{Annals of Statistics}, Vol. 37, No. 3, 1150-1171.
	
	\bibitem{BKMP} Baldi, P.; Kerkyacharian, G.; Marinucci, D.; Picard, D. (2009). Subsampling Needlet Coefficients on the Sphere, \textit{Bernoulli}, Vol. 15, 438-463.
	
	\bibitem{Baldi2} Baldi, P.; Trapani, S. (2015) Fourier coefficients of invariant random fields on homogeneous spaces of compact Lie groups, \textit{Ann. Inst. Henri Poincar\'e Probab. Stat. }51, no. 2, 648-671.
	
	
%	\bibitem{Barnett} Barnett, J. T. (2001). \textit{Zero-Crossings of Random Processes with Application to Estimation Detection}. In Marvasti, Farokh A. Nonuniform Sampling: Theory and Practice. Springer. ISBN 0306464454.
	
	\bibitem{BG} Beffara, V.; Gayet, D. (2017). Percolation of random nodal lines. Publ. \textit{Math. Inst. Hautes Etudes} Sci. 126, 131-176.
	
	\bibitem{BMW} Benatar, J.; Marinucci, D.; Wigman I. (2017) Planck-scale distribution of nodal length of arithmetic random waves, preprint,
	arXiv:1710.06153.
	
	\bibitem{berard} Berard, P. (1985) Volume des ensembles nodaux des fonctions propres du laplacien. (French) [Volume of the nodal sets of eigenfunctions of the Laplacian] Bony-Sjöstrand-Meyer seminar, 1984–1985, Exp. No. 14 , 10 pp., École Polytech., Palaiseau, 1985. 
	
	\bibitem{berry} Berry, M. V. (2002) Statistics of nodal lines and points in chaotic quantum billiards: perimeter corrections, fluctuations, curvature, \textit{J. Phys. }A 35, no. 13, 3025–3038. 
	
	\bibitem{Berry1977} Berry, M. V. (1977) Regular and irregular semiclassical wavefunctions. \textit{J. Phys.} A 10, no. 12, 2083–2091. 81.58.
	
	\bibitem{BSZ} Bleher, P.; Shiffman, B.; Zelditch, S. (2000) Universality and scaling of correlations between zeros on complex manifolds \textit{Invent. Math.} 142, no. 2, 351-395.
	
	\bibitem{BSZ2} Bleher, P.; Shiffman, B.; Zelditch, S. (2001). Universality and scaling of zeros on symplectic manifolds Random matrix models and their applications, 31-69, \textit{Math.Sci. Res. Inst. Publ.}, 40, Cambridge Univ. Press, Cambridge.
	
	%	\bibitem{Bo}  Bourgain, J. On toral eigenfunctions and the random wave model. Israel \textit{J. of Math.} 201, no. 2 (2014): 611-630.
	
	%	\bibitem{Br}  Br\"{u}ning, J. Uber Knoten Eigenfunktionen des Laplace-Beltrami Operators, Math. Z.	158 (1978), 15-21.
	
	%\bibitem{BG} Br\"{u}ning, J.; Gromes, D. Uber die L\"{a}nge der Knotenlinien schwingender Membranen, Math. Z. 124 (1972), 79-82.
	
	\bibitem{BR11} Bourgain, J., Rudnick, Z. (2011) On the geometry of the nodal lines of eigenfunctions on the two-dimensional torus,\textit{ Ann.
		Henri Poincar\'e }12, no. 6, 1027-1053.
	
	\bibitem{brockwell and davis} Brockwell, P. J.; Davis, R. A. (1996) \textit{Introduction to Time Series and Forecasting}, Springer-Verlag, New York, Inc.
	
	
	\bibitem{BW2016} Buckley, J.; Wigman, I. (2016)
	On the number of nodal domains of toral eigenfunctions. (English summary),
	\textit{Ann. Henri Poincar\'e 17}, no. 11, 3027-3062.
	
	%\bibitem{C2014} Chatterjee, Sourav A short survey of Stein's method. Proceedings of the International Congress of Mathematicians Seoul 2014. Vol. IV, 1-24, Kyung Moon Sa, Seoul, 2014.
	
	%	\bibitem{C2008}	Sourav Chatterjeear, A new method of normal approximation. Xiv:math/0611213.
	
	\bibitem{C} Cammarota, V. (2017) Nodal Area Distribution For Arithmetic Random
	Waves, arXiv:1708.07679v1.
	
	
	\bibitem{CM}  Cammarota, V.; Marinucci, D. (2018) A Quantitative Central Limit Theorem for the Euler-Poincaré Characteristic of Random Spherical Eigenfunctions. \textit{Annals of Probabability }46, no. 6, 3188–3228.
	
	\bibitem{CM2015} Cammarota, V.; Marinucci, D., (2015) On the limiting behavior of Needlets Plyspectra, (English, French summary) 
	\textit{Ann. Inst. Henri Poincaré Probab. Stat.} 51, no. 3, 1159–1189. 
	
	\bibitem{CMW} Cammarota, V.; Marinucci, D.; Wigman, I. (2016) Fluctuations of the Euler-Poincar\'e characteristic for random spherical harmonics,
	\textit{Proceedings of the American Mathematical Society}, 11, 4759-4775.
	
	
	
	\bibitem{CMW2016} Cammarota, V.; Marinucci, D.; Wigman, I. (2016) On the distribution of the critical values of random spherical harmonics,
	\textit{Journal of Geometric Analysis}, 4, 3252-3324.
	
	
	\bibitem{C2009} Chatterjee, S. (2009) Fluctuations of eigenvalues and second order Poincar\'e inequalities. \textit{Probab. Theory Related Fields} 143, no. 1-2, 1–40. 
	
%	\bibitem{cheng} Cheng, D. (2017) Excursion probabilities of isotropic and locally isotropic gaussian random fields on manifolds, \textit{Extremes} 20, no. 2, 475–487.
	
	
%	\bibitem{cheng2} Cheng, D. (2015) Excursion probability of certain non-centered smooth gaussian random fields, Preprint (ArXiv 1502.04414).
	
	\bibitem{Cheng} Cheng, S. Y. (1976) Eigenfunctions and nodal sets, 	\textit{Comm. Math. Helv.} 51, no. 1, 43–55. 
	
	
%	\bibitem{CS}Cheng, D.; Schwartzman, A. (2015) On the explicit height distribution and expected number of local maxima of isotropic gaussian random fields, Preprint (ArXiv1503.01328).
	
%	\bibitem{CX} Cheng, D.; Xiao, Y. (2012) The mean euler characteristic and excursion probability of gaussian random fields with stationary increments, Preprint (ArXiv 1211.6693).
	
	%	\bibitem{Mau 2014} Cheng, D.; Xiao, Y. (2016) Excursion probability of gaussian random fields on sphere, \textit{Bernoulli} 22, no. 2, 1113–1130.
	
	
	\bibitem{cramer and leadbetter} Cramér, H.; Leadbetter, M. R. (1967), \textit{Stationary and related stochastic processes}, Wiley, New York.
	
	
	\bibitem{DNPR} Dalmao, F.; Nourdin, I.; Peccati, G.; Rossi, M. (2016) Phase Singularities in Complex	Arithmetic Random Waves. arXiv:1608.05631v3.
	
	\bibitem{DF} Donnelly, H.; Fefferman, C.  (1988) Nodal sets of eigenfunctions on Riemannian manifolds,
	\textit{ Invent. Math.} 93, 161-183.
	
	\bibitem{FHMM} Fantaye, Y.; Hansen, F.K.; Maino, D.; Marinucci, D. (2015) Cosmological Applications of the Gaussian Kinematic Formula, \textit{Physical Review D}, Volume 91, 063501.
	
	\bibitem{GM} Geller, D.; Mayeli, A. (2009) Continuous Wavelets on Manifolds, \textit{Math. Z.}, Vol. 262, pp. 895-927.
	
	\bibitem{GW16}  Granville, A.; Wigman, I. (2017) Planck-scale mass equidistribution of toral Laplace eigenfunctions. \textit{Comm. Math. Phys.}, 355, no. 2, 767–802.
	
	\bibitem{KKW} Krishnapur, M.; Kurlberg P.; Wigman, I. (2013) Nodal length
	fluctuations for arithmetic random waves. \textit{Annals of Mathematics} (2)
	177, no. 2, 699-737.
	
	
	
%	\bibitem{KW} Krishnapur M.; Wigman I. Fluctuations of the nodal length of random eigenfunction of the Laplace ont he torus.  
	
	\bibitem{LMX} 
	Lan, X.; Marinucci, D.; Xiao, Y. (2018) Strong local nondeterminism and exact modulus of continuity for spherical Gaussian fields.
	\textit{Stochastic Process. Appl.} 128, no. 4, 1294-1315. 
	
	
	\bibitem{Lang e Schwab} Lang, A.; Schwab, C. (2015) Isotropic Gaussian random fields on the sphere: regularity, fast simulation and stochastic partial differential equations. \textit{Ann. Appl. Probab.} 25, no. 6, 3047-3094.
	
	\bibitem{LeRu}  Lester, S.; Rudnick, Z. (2017) Small scale equidistribution of eigenfunctions on the torus, \textit{Comm. Math. Phys.}, 350 (1), 279-300.
	
	\bibitem{13} Lewis, A. (2012) The full squeezed CMB bispectrum from inflation. \textit{Journal of Cosmology and Astroparticle Physics}, 06, 023. 
	
	\bibitem{Logunov b} Logunov, A. (2018) Nodal sets of Laplace eigenfunctions: polynomial upper estimates of the Hausdorff measure. \textit{Ann. of Math.} (2) 187, no. 1, 221-239.
	
	\bibitem{Logunov a} Logunov, A. (2018) Nodal sets of Laplace eigenfunctions: proof of Nadirashvili's conjecture and of the lower bound in Yau's conjecture. \textit{ Ann. of Math. }(2) 187, no. 1, 241-262.
	
	\bibitem{LM} Logunov, A.; Malinnikova, E. (2015) On ratios of harmonics functions. \textit{Adv. Math.} 274, 241-262. 
	
	
	%	\bibitem{Malyarenko1}Malyarenko, A. Invariant random fields in vector bundles and application to cosmology, Ann. Inst. Henri Poincar´e Probab. Stat. 47 (2011), no. 4, 1068?1095. MR 2884225 (2012k:60151)
	
	
	%	\bibitem{Malyarenko2}, Invariant random fields on spaces with a group action, Probability and its Applications (New York), Springer, Heidelberg, 2013, With a foreword by Nikolai Leonenko. MR 2977490
	\bibitem{M2008} Marinucci, D. (2008) A Central Limit Theorem and Higher Order Results for the Angular Bispectrum, \textit{Probability Theory and Related Fields}, Vol. 141, N.3-4, pp. 389-409, math.pr/0509430.
	
	\bibitem{M2006} Marinucci, D. (2006) High Resolution Asymptotics for the Angular Bispectrum of Spherical Random Fields, \textit{Annals of Statistics}, Vol.34, N.1, pp. 1-4.
	
	\bibitem{Marinucci} Marinucci, D. (2015) Lecture Notes on Spherical Random Fields. Lecture notes, Finnish School in Probability and Statistics, June 2015.
	
	
	\bibitem{M e P 2013} Marinucci, D.; Peccati, G. (2013) Mean-square continuity on homogeneous spaces of compact groups. (English summary) 
	\textit{Electron. Commun. Probab.} 18, no. 37, 10 pp.
	
	\bibitem{M e Peccati}  Marinucci, D.; Peccati, G. (2011) \textit{Random fields on the sphere. Representation, limit theorems and cosmological applications}. London Mathematical Society Lecture Note Series, 389. Cambridge University Press, Cambridge. 
	
	
	\bibitem{MPRW} Marinucci, D.; Peccati, G.; Rossi, M.; Wigman, I. (2016)
	Non-universality of nodal length distribution for arithmetic random waves. (English summary)
	\textit{Geom. Funct. Anal.} 26, no. 3, 926-960.
	
	\bibitem{M e Mau 2015} Marinucci, D.; Rossi, M. (2015) Stein-Malliavin approximations for nonlinear functionals of random eigenfunctions on $\mathbb{S}^d$. \textit{J. Funct. Anal. }268, no. 8, 2379-2420. 
	
	%	\bibitem{MRW} Marinucci D., Rossi M., Wigman I. Nodal length of random spherical harmonics (2017) arXiv:1705.05747.
	
	
	\bibitem{MRW2017} Marinucci, D.; Rossi, M.; Wigman, I. (2017) The asymptotic
	equivalence of the sample trispectrum and the nodal length for random
	spherical harmonics, preprint, arXiv:1705.05747.
	
	
%	\bibitem{M e Vadlamani} Marinucci, D.; Vadlamani, S. (2015) A note on global suprema of band-limited spherical random functions. \textit{Statist. Probab. Lett.} 96, 141-148.
	
	
	\bibitem{MV} Marinucci, D.; Vadlamani, S. (2016) High-Frequency Asymptotics for Lipschitz-Killing Curvatures of Excursion Sets on the Sphere. \textit{Ann. Appl. Probab.} 26, no. 1, 462-506. 
	
	
	
	\bibitem{M e W 2012} Marinucci, D.; Wigman, I. (2014) On nonlinear functionals of
	random spherical eigenfunctions. \textit{Comm. Math. Phys.} 327, no. 3,
	849-872.
	
	\bibitem{M e W 2011} Marinucci, D.; Wigman, I. (2011) On the excursion sets of spherical Gaussian eigenfunctions. \textit{J. Math. Phys.} 52, no. 9, 093301, 21 pp.
	
	\bibitem{M e W 2011bis} Marinucci, D.; Wigman, I. (2011) The Defect Variance of Random Spherical Harmonics. \textit{Journal of Physics A: Mathematical and Theoretical}, 44, 355206.
	
	\bibitem{Matsubara} Matsubara, T. (2010) Analytic Minkowski functionals of the Cosmic Microwave Background: second-order non-Gaussianity with bispectrum and trispectrum. \textit{Phys. Rev. D} 81, 083505.
	
	\bibitem{NPW2} Narcowich, F. J.; Petrushev, P.; Ward, J.D. (2006) Decomposition of Besov and Triebel-Lizorkin spaces on the sphere, \textit{Journal of Functional Analysis}, 238, 2, 530-564.
	
	\bibitem{NPW} Narcowich, F. J.; Petrushev, P.; Ward, J.D. (2006) Localized tight frames on spheres, \textit{SIAM Journal of Mathematical Analysis}, 38, 2, 574-594.
	
	
	
	\bibitem{N} Neuheisel, J. (2000) The asymptotic distribution of nodal sets on spheres, Johns Hopkins
	Ph.D. thesis.
	
	\bibitem{Peccati Nourdin} Nourdin, I.; Peccati, G. (2012) \textit{Normal approximations with Malliavin calculus. From Stein's method to universality.} Cambridge Tracts in Mathematics, 192. Cambridge University Press, Cambridge. 
	
	\bibitem{NP2009} Nourdin, I.; Peccati, G. (2010) Stein's method meets Malliavin calculus: a short survey with new estimates. Recent development in stochastic dynamics and stochastic analysis, 207–236, \textit{Interdiscip. Math. Sci.}, 8, World Sci. Publ., Hackensack, NJ, 2010.
	
	\bibitem{NPR} Nourdin, I.; Peccati, G.; Rossi, M. (2017) Nodal Statistics of
	Planar Random Waves. arXiv:1708.02281v1.
	
	
	
	%\bibitem{ORW} Oravecz, F., Rudnick, Z., Wigman, I. The Leray measure of nodal sets for random eigenfunctions on the torus, Ann. Inst. Fourier (Grenoble) 58 (2008), 299-335.
	
	
	
	
	
	%\bibitem{M e W 2011bis} Domenico Marinucci and Igor Wigman (2011), The Defect Variance of Random Spherical Harmonics,
	%Journal of Physics A: Mathematical and Theoretical, 44, 355206.
	
	
	\bibitem{PR2017} Peccati, G.; Rossi, M. (2017). Quantitative limit theorems for local functionals of arithmetic random waves. \textit{Computation and Combinatorics in Dynamics, Stochastics and Control, The Abel Symposium 2016} – Springer (in press).  arXiv:1702.03765v1.
	
	\bibitem{PTudor}Peccati, G.; Tudor, C.A. (2007) Anticipating integrals and martingales on the Poisson space, \textit{Random Oper. Stoch. Equ.} 15, no. 4, 327–352. 
	
%	\bibitem{P e T} Peccati, G.; Taqqu, M.S. (2011) Wiener Chaos: Moments, Cumulants and Diagrams, Springer-Verlag.
	
	\bibitem{Planck 2015} Planck 2013 results. XXIV. Constraints on primordial non-Gaussianity (Planck Collaboration), \textit{Astronomy and Astrophysics},  Volume 571, idA24, 58 pp. (2014).
	
	\bibitem{Planck 2014} Planck 2013 results. XXIII. Isotropy and statistics of the CMB (Planck Collaboration), \textit{Astronomy and Astrophysics},  Volume 571, idA23. (2014)
	
	\bibitem{Rossi2} Rossi, M. (2018) Random Nodal Lengths and
	Wiener Chaos. \textit{Proceedings of the Workshop “Probabilistic Methods in Spectral Geometry and PDE” in Montréal, August 2016} (to appear). arXiv:1803.09716.
	
	\bibitem{Rossi} Rossi, M. (2016) The defect of random hyperspherical harmonics, \textit{Journal of Theoretical Probability} (in press). arXiv:1605.03491.
	
	
	\bibitem{mau} Rossi, M. (2016) The geometry of spherical random fields - PhD thesis. arXiv:1603.07575.
	
	
	%\bibitem{Rossi} Rossi On the high-energy defect distribution for random hyperspherical harmonics
	

	
	\bibitem{RossiW} Rossi, M.; Wigman, I. (2018) Asymptotic distribution of nodal intersections for arithmetic random waves. \textit{Nonlinearity} 31, no. 10, 4472-4516. 
	
	
	
	\bibitem{RW} Rudnick, Z.; Wigman I. (2016) Nodal intersections for random
	eigenfunctions on the torus, \textit{American Journal of Mathematics}, 138, no. 6,
	1605-1644.
	
	\bibitem{RW2} Rudnick, Z.; Wigman, I. (2008) On the volume of nodal sets for eigenfunctions of the Laplace on the torus, \textit{annales Henri Poincar\'e}, Vol.9, No 1, 109-130.
	
	\bibitem{RWY} Rudnick, Z.; Wigman, I.; Yesha N. (2015) Nodal intersections for
	random waves on the 3-dimensional torus, \textit{Annales Institut Fourier}, 66, no.
	6, 2455-2484.
	
	\bibitem{Schoenberg (1942)}Schoenberg, I.J. (1942) Positive definite functions on spheres. \textit{Duke math. J.} 9, 96-108.
	
	
	
	\bibitem{szego} Szego, G. (1975) Orthogonal polynomials, Fourth edition. \textit{%
		American Mathematical Society, Colloquium Publications, Vol. XXIII.} \textit{%
		American Mathematical Society, Providence, R.I.}
	
	\bibitem{AP1} Todino, A. P. (2018) A Quantitative Central Limit Theorem for the Excursion Area of
	Random Spherical Harmonics over Subdomains of $\mathbb{S}^2$. arXiv:1807.06982
	
	\bibitem{AP2} Todino, A. P. (2018) Nodal Lengths in Shrinking Domains for Random Eigenfunctions on $\mathbb{S}^2$. arXiv:1807.11787.
	
%	\bibitem{Triebel} Triebel, H. (1995). \textit{Interpolation Theory, Function Spaces, Differential Operators}, 2nd ed. Johann Ambrosius Barth, Heildelberg.
	
%	\bibitem{TW} Toth John A.; Wigman I. (2009) Universality of length distribution of nodal lines of random waves on generic surfaces.
	
	%\bibitem{VMK} Varshalovich D.A., A.N. Moskalev, and Khersonskii V.K. (1988), Quantum Theory of Angular Momentum, World Scientific.
	
	\bibitem{quantum theory} Varshalovich, D. A.; Moskalev, A. N.; Khersonski,
	V. K. (1988) \textit{Quantum theory of angular momentum. Irreducible tensors,
		spherical harmonics, vector coupling coefficients, 3nj symbols}. Translated
	from the Russian. World Scientific Publishing Co., Inc., Teaneck, NJ.
	
	
	
	
	\bibitem{Wigman2} Wigman, I. (2011) On the nodal lines of random and deterministic Laplace eigenfunctions, \textit{Spectral geometry}, \textit{Proc. Sympos. Pure Math.}, vol. 84, \textit{Amer. Math. Soc.}, \textit{Providence, RI}, 2012, pp. 285-297. 
	
	\bibitem{W} Wigman, I. 	(2010) Fluctuations of the nodal length of random spherical
	harmonics, \textit{Communications in Mathematical Physics, 398 no. 3 787-831}.
	
	\bibitem{35} Wigman, I. (2009) On the distribution of the nodal sets of random
	spherical harmonics. \textit{Journal of Mathematical Physics}, 50, no. 1,
	013521, 44 pp.
	
%	\bibitem{W1} Wigman I., Volume fluctuations of the nodal sets of random Gaussian subordinated spherical harmonics.
	
	
	
	
	
	% \bibitem{RW} Rudnick, Z., Wigman I.; Nodal intersections for random eigenfunctions on the torus, \textit{American Journal of Mathematics, 138, no. 6}, 1605-1644 (2016).
	
	
	%\bibitem{mau} Maurizia Rossi(2015), the defect of random hyperspherical harmonics
	
	%\bibitem{szego} Szego Gabor (1975), Orthogonal polynomials, Fourth edition. American Mathematical Society, Colloquium Publications, Vol. XXIII. American Mathematical Society, Providence, R.I.
	
	%\bibitem{quantum theory} D.A Varshalovich, A.N. Moskalev, V.K. Khersonskii (1988), Quantum theory of angular momentum, World Scientific.
	
	
	\bibitem{Y1982}  Yau, S.T. (1982) Survey on partial differential equations in differential geometry. Seminar
	on Differential Geometry, pp. 3-71, \textit{Ann. of Math. Stud.}, 102, Princeton Univ. Press,
	Princeton, N.J.
	
	\bibitem{Y1990} Yau, S.T. (1993) Open problems in geometry. Differential geometry: partial differential equations
	on manifolds (Los Angeles, CA, 1990), 1-28, \textit{Proc. Sympos. Pure Math.}, 54,
	Part 1, \textit{Amer. Math. Soc.}, \textit{Providence, RI}.
	
%	\bibitem{Ylvisaker} Ylvisaker N. D. (1965). The Expected Number of Zeros of a Stationary Gaussian Process. \textit{The Annals of Mathematical Statistics.} 36 (3): 1043. doi:10.1214/aoms/1177700077.
	
	
	
	
	%	\bibitem{Wigman1}Igor Wigman, Fluctuations of the nodal length of random spherical harmonics, Comm. Math. Phys. 298 (2010), no. 3, 787?831. MR 2670928 (2012f:58073)
	
	
	%\bibitem{mall}Normal approximations with Malliavin calculus. 

\end{thebibliography} 
